Orchestrating stencils with the Multi-Stencil Framework

### 2017-02-24 ARTICLES/IJPP/articleR1/conclusion.tex
evaluation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% unifier texte avec nouvelle version article
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have presented the Multi-Stencil Language (MSL), a domain specific language for stencil-based numerical simulations. Compared to other existing stencil DSLs, MSL proposes a higher abstraction level for end-users. MSL offers a way to describe a numerical simulation independently from the type of mesh used. As a result, the language can be used for a larger number of simulations. It helps to clearly separate the description of the simulation from implementation choices, which facilitates reuse of existing languages and libraries, for example languages for data structures optimizations and parallelization strategies.

In this paper, the formal definition of a multi-stencil program has been given. This formalism helps to understand what is defined into the light grammar of MSL, and also how parallelization can be extracted from it. MSL produces an empty parallel pattern of the numerical simulation described. This pattern indicates where synchronizations are needed, but not how they are performed, which is dependent from the type of mesh and from implementation choices. This second step is left to other existing languages, which are chosen as a back-end of MSL. For example, in this paper the chosen back-end is a code using SkelGIS~\cite{CPE:CPE3494,DBLP:conf/ieeehpcs/HeleneS13,DBLP:conf/europar/CoullonL14}, a templated C++ language for distributed meshes (using MPI), and OpenMP~\cite{660313}.

Experiments presented in this paper show that the back-end code produced by MSL, \ie by a mesh-agnostic language, does not introduce overheads up to 16.384 cores, and that the hybrid (data and task) parallelism automatically introduced by the language, which combines SkelGIS and OpenMP as a back-end, improves performance compared to a data parallelization only. Thus, with the same code asked to the user, two different parallel versions of the simulation can be obtained.

However, if performances are improved by the hybrid parallelization, this performance is also limited by the scheduling strategy used in this paper. Actually, as described in Section~\ref{sect:msp}, a static series-parallel (fork-join) scheduling is performed in this work. This helps to define a predictive performance model, which has been validated in experiments. However, getting rid of global synchronizations (join) could be an interesting improvement to get better performance, especially for irregular simulations, where tasks are not naturally balanced. Our immediate perspective, thus, is to use OpenMP dynamic schedulers~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359} as back-ends to study performance improvments. Using such dynamic schedulers also opens to more heterogeneous architectures, such as GPUs or many-cores accelerators.

Finally, to validate the separation of concerns introduced by MSL, a second back-end for unstructured meshes could be interesting. We think about PaMPA~\cite{lachat:hal-00768916} as a distributed data structure backend, instead of SkelGIS. Thus using a single language, the MSL language, two different kinds of numerical simulations could be defined: one onto Cartesian meshes; and one on unstructured meshes.

>>>>

%We have presented the Multi-Stencil Language (MSL), a domain specific language for stencil-based numerical simulations. Compared to other existing stencil DSLs, MSL proposes a higher abstraction level for end-users. MSL offers a way to describe a numerical simulation independently from the type of mesh used. As a result, the language can be used for a larger number of simulations. It helps to clearly separate the description of the simulation from implementation choices, which facilitates reuse of existing languages and libraries, for example languages for data structures optimizations and parallelization strategies.

%In this paper, the formal definition of a multi-stencil program has been given. This formalism helps to understand what is defined into the light grammar of MSL, and also how parallelization can be extracted from it. MSL produces an empty parallel pattern of the numerical simulation described. This pattern indicates where synchronizations are needed, but not how they are performed, which is dependent from the type of mesh and from implementation choices. This second step is left to other existing languages, which are chosen as a back-end of MSL. For example, in this paper the chosen back-end is a code using SkelGIS~\cite{CPE:CPE3494,DBLP:conf/ieeehpcs/HeleneS13,DBLP:conf/europar/CoullonL14}, a templated C++ language for distributed meshes (using MPI), and OpenMP~\cite{660313}.

E%xperiments presented in this paper show that the back-end code produced by MSL, \ie by a mesh-agnostic language, does not introduce overheads up to 16.384 cores, and that the hybrid (data and task) parallelism automatically introduced by the language, which combines SkelGIS and OpenMP as a back-end, improves performance compared to a data parallelization only. Thus, with the same code asked to the user, two different parallel versions of the simulation can be obtained.

%However, if performances are improved by the hybrid parallelization, this performance is also limited by the scheduling strategy used in this paper. Actually, as described in Section~\ref{sect:msp}, a static series-parallel (fork-join) scheduling is performed in this work. This helps to define a predictive performance model, which has been validated in experiments. However, getting rid of global synchronizations (join) could be an interesting improvement to get better performance, especially for irregular simulations, where tasks are not naturally balanced. Our immediate perspective, thus, is to use OpenMP dynamic schedulers~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359} as back-ends to study performance improvments. Using such dynamic schedulers also opens to more heterogeneous architectures, such as GPUs or many-cores accelerators.

%Finally, to validate the separation of concerns introduced by MSL, a second back-end for unstructured meshes could be interesting. We think about PaMPA~\cite{lachat:hal-00768916} as a distributed data structure backend, instead of SkelGIS. Thus using a single language, the MSL language, two different kinds of numerical simulations could be defined: one onto Cartesian meshes; and one on unstructured meshes.

### 2017-02-24 ARTICLES/IJPP/articleR1/evaluation.tex
evaluation

We define the \emph{level of parallelism} as the number of parallel tasks inside a fork of the fork/join model.

Table~\ref{fig:freq} represents the number of time a given level of parallelism, \ie the number of tasks to perform concurrently, is observed in the final tree. One can notice that the level of task parallelism extracted from the Shallow water equations is limited by two sequential parts in the application (level 1). Moreover, a level of 16~parallel tasks is reached two times, and five times for the fourth level.
This means that if two threads are dedicated to task parallelism, two parts of the code at least will not take advantage of this and that no part of the code would benefit from more than 16 threads.
The task parallelism alone is therefore clearly not enough to take advantage of even a single node of a cluster that typically supports today between 16 and 32 threads (16 for Curie).

@@

@@

On the other hand, Figure~\ref{fig:limit} illustrates limitations of data parallelization technique alone.
While the computation time decreases linearly with the number of core used, the communication behavior is much more erratic.
Between 2 and 16 cores, the communication happen inside a single node and the time is small and nearly constant.
There is a small oscillation that might be explained by difference between number of processors that are power of 4, where the communications are all the same, and those that are nota power of 4, where there is an imbalance.
Starting with 32 cores, there are multiple nodes and the communication time is typically modeled as $L+S/B$ where $L$ is the latency, $S$ the data size and $B$ the bandwidth.
This explains the decrease of time from 32 to 128 cores where the data sizes communicated by each process decreases.
The increased observed after that might be due to the fact that with the increased number of processes the fat-tree becomes deeper and the latencies increase.

@@

All in all, when the number of core used increases, the computation/communication ratio becomes poorer and poorer.
As a result, the data parallelism alone fails to provide enough parallelism to leverage the whole machine and other sources of parallelism have to be found.
The blue curve of Figure~\ref{fig:close} shows the total execution time for the same example as in Figure~\ref{fig:limit} and as expected, the speedup bends down from 256 to 2048 cores.

In addition to the blue curve, Figure~\ref{fig:close} shows strong scalings for the same example but using an hybrid parallelization. For example, the purple curve shows the parallelization which uses 8 cores, to perform the task parallelization, for each process used for data parallelization (\ie MPI process). As a result, for example, when using 2 machines of the TGCC cluster, with a total of 32 cores, 4 cores are used for SkelGIS MPI processes, for data parallelization, and for each one 8 cores are used for task parallelization ($4 \times 8 = 32$).

As a result, and as explained in Section~\ref{sect:perfs}, data is less divided into sub-domains and the effect which is observe onto the blue curve is delayed. This figure shows a comparison with 2, 4, 8 and 16 cores per MPI process for task parallelization.

From 2 to 8 cores, the improvement of the strong scaling is clear. However, reaching 16 cores, an important initial overhead appears and in addition to this, the curve bends down rapidly instead of improving the one with 8 cores for task parallelization. Two different phenomena happen.

First, thin nodes of the TGCC Curie are built with two NUMA nodes each of 8 cores. As a result, when increasing the number of OpenMP cores for task parallelization from 8 to 16 cores, an overhead is introduced by exchanges of data between memories of the two NUMA nodes. This phenomena is illutrated in Figure~\ref{fig:spread}. In this figure, a different strategy is used to bind threads onto available cores (using OpenMP). This strategy, called \emph{spread} (instead of \emph{close} in Figure~\ref{fig:close}), binds threads on cores in order to spread as much as possible onto resources, which means that the two NUMA nodes are directly used whatever the number of cores kept for task parallelization. As a result, and as shown in the figure, using 2, 4 and 8 cores an initial overhead is introduced.

@@

The second phenomena, which happens in Figure~\ref{fig:close} with 16 cores for tasks parallelization, is due to the level of parallelization introduced by the task parallelization technique. Actually, as illustrated in Table~\ref{fig:freq}, only two steps of the $TSP$ static scheduling generated by the MSL compiler can take advantage of 16 cores among a total of 18 steps. This phenomena has been explained in Section~\ref{sect:perfs} by the variable $F_{task}$ and the fact that it is not always true that $F_{task}=P_{task}$. This explains why using 16 cores for task parallelization in Figure~\ref{fig:spread} is still less efficient than using 8 cores even if the two NUMA nodes are always used in this evaluation.

Finally, to completely validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{fig:tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case (\ie when 8 cores are used for task parallelization), and with a \emph{close} OpenMP bind of threads onto cores. Table~\ref{fig:tth} gives time details.

@@

Figure~\ref{fig:tth2} and Table~\ref{fig:tth} perfectly matches results observed in Figure~\ref{fig:close} for 8 cores used for task parallelization per core used for data parallelization. As a result, the hybrid parallelization becomes better with a total of 512 cores.

>>>>

We define the \emph{level of parallelism} as the number of parallel tasks inside one fork of the fork/join model. The fork/join model obtained for FullSWOF2D is composed of 18 fork phases (corresponding to $\mathcal{P}$ nodes of $TSP$). Table~\ref{fig:freq} represents the number of time a given level of parallelism is obtained inside fork phases.

@@

One can notice that the level of task parallelism extracted from the Shallow water equations is limited by two sequential parts in the application (level 1). Moreover, a level of 16~parallel tasks is reached two times, and five times for the fourth level.
This means that if two cores are dedicated to task parallelism, the two sequential parts of the code will not take advantage of these two cores, and that no part of the code would benefit from more than 16 cores. The task parallelism, as proposed in this paper (\ie where each kernel is a task) is therefore not insufficient to take advantage of a single node of modern clusters that typically supports more than 16 cores.

@@

On the other hand, Fig.~\ref{fig:limit} illustrates limitations of data parallelization technique alone. In this figure is represented the execution time (with a logarithmic scale) of FullSWOF2D while increasing the number of cores for a fix domain size of $500 \times 500$ with a total of $200$ time iterations (\ie this is a strong scaling). The speedup of this same benchmark is represented in blue in Fig.~\ref{fig:close}. One can note that the scaling is not as good is the one presented in Fig.~\ref{fig:strong}. 
The main difference between these two benchmarks is the domain size. In the benchmark of Fig.~\ref{fig:strong} the domain size is $10k \times 10k$ which means that using $2^8$ cores, for example, each core has to compute only a $31 \times 31$ sub-domain. On the other hand using $2^8$ cores in Fig.~\ref{fig:close} each core has to compute a $625 \times 625$ sub-domain. Fig.~\ref{fig:limit} shows why the speedup is not as good as the one with a bigger domain size.

Actually, in this figure, while the computation time (in blue) decreases linearly with the number of core used, the communication behavior (in red) is much more erratic. Between 2 and 16 cores, communications are performed inside a single node thus the time is small and nearly constant. There is a small oscillation that might be explained by the partitioning differences. SkelGIS performs a two dimensional partitioning strategy. For this reason a smaller number of bytes are communicated using 2 cores than using 4, and using 8 cores than using 16 cores. Starting from 32 cores, each node is fully used and more than one node is used. From this point thus the communication time is typically modeled as $L+S/B$ where $L$ is the latency, $S$ the data size and $B$ the bandwidth. This explains the decrease of time from 32 to 128 cores where the data sizes communicated by each process decreases. The increased observed after$128$ cores that might be due to the fact that with the increased number of processes the fat-tree becomes deeper and the latencies increase.

@@

All in all, when the number of core used increases, the computation/communication ratio becomes poorer and poorer. As a result, the data parallelism alone fails to provide enough parallelism to leverage the whole machine and other sources of parallelism have to be found. As expected, in  Figure~\ref{fig:close} the speedup bends down from 256 to 2048 cores. The same problem would happened in previous experiment of Fig.~\ref{fig:strong}, however as the domain size is larger, the phenomena appears with much more cores.

As task parallelism fails to scale from 16 cores, and as data parallelism also fails to scale when the communication cost overpass the execution time, an hybrid parallelization strategy is proposed by MSF and evaluated below.

In addition to the blue curve, Fig.~\ref{fig:close} shows speedups for the same example ($500 \times 500$ domain with $200$ iterations) but using an hybrid parallelization. Fig.~\ref{fig:close} shows a comparison with 2, 4, 8 and 16 cores per MPI process for task parallelization.

For example, the purple curve shows the parallelization which uses for each data parallelization process (\ie MPI process) 8 additional cores for task parallelization. As a result, for example, when using 2 machines of the TGCC cluster, with a total of 32 cores, 4 cores are used for SkelGIS MPI processes, for data parallelization, and for each one 8 cores are used for task parallelization ($4 \times 8 = 32$). This respect $P = P_{data} \times P_{task}$ presented in Section~\ref{sect:perfs}.
As a result, and as explained in Section~\ref{sect:perfs}, quantities are less divided into sub-domains, that are responsible for communications, and the effect which is observe onto the blue curve is delayed.

From 2 to 8 cores, the improvement of the strong scaling is clear. However, reaching 16 cores, an important initial overhead appears and in addition to this, the curve bends down rapidly instead of improving the one with 8 cores for task parallelization. Two different phenomena happen in this case.

First, thin nodes of the TGCC Curie are built with two NUMA nodes each of 8 cores. As a result, when increasing the number of OpenMP cores for task parallelization from 8 to 16 cores, an overhead is introduced by exchanges of data between memories of the two NUMA nodes. This phenomena is illutrated in Fig.~\ref{fig:spread}. In this figure, a different binding strategy is used. A binding strategy is the way the scheduler binds threads onto available cores. The strategy used in Fig.~\ref{fig:spread} is called \emph{spread} (instead of \emph{close} in Figure~\ref{fig:close}). This strategy binds threads on cores in order to spread as much as possible onto resources, which means that the two NUMA nodes are directly used whatever the number of cores used for task parallelism. As a result, and as shown in the figure, using 2, 4 and 8 cores an initial overhead is introduced as the one observed in Fig.~\ref{fig:close}. This shows that the initial overhead with 16 cores is due to NUMA effects.

@@

The second phenomena that happens in Figure~\ref{fig:close} using 16 cores is due to the level of parallelism introduced by the task parallelization technique. Actually, as illustrated in Table~\ref{fig:freq}, only two forks of $TSP$ can take advantage of 16 cores among a total of 18 forks. This phenomena has been mentioned in Section~\ref{sect:perfs} by the variable $F_{task}$ and the fact that it is not always true that $F_{task}=P_{task}$. This explains why using 16 cores is less efficient than using 8 cores, even when the two NUMA nodes are always used as in Fig.~\ref{fig:spread}.

Finally, to validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{fig:tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case, \ie when 8 cores are used in Fig.~\ref{fig:close}.  Figure~\ref{fig:tth2} and Table~\ref{fig:tth} presents results of these measurements. Results perfectly matches Fig.~\ref{fig:close} for 8 cores per MPI process. As a result, the hybrid parallelization becomes better with a total of 512 cores in this case.

@@

### 2017-02-24 ARTICLES/IJPP/articleR1/introduction.tex
evaluation

As the computation power of modern high performance architectures increases, their heterogeneity and complexity also become more important. For example, the current world's top supercomputer Tianhe-2~\footnote{\url{www.top500.org}} is composed of multi-cores processors and accelerators, and is able to reach a theoretical peak performance around thirty peta floating point operations par seconds. However, to be able to use such a machine, multiple programming models, such as MPI (Message Passing Interface), OpenMP, CUDA etc., and multiple optimization techniques, such as cache or vectorization optimizations, have to be combined. Moreover, current architectures evolution lets think that heterogeneity and complexity in HPC will continue to grow in future.

One of the big challenges to solve to be able to use exascale computers is to propose programming models which gives access to high performance computing (HPC) to many scientists and not only to a few HPC specialists~\cite{ETP4HPC2013}. Actually, applications which run on supercomputers and which need such a computation power are physics, weather or genomic applications, which are not implemented by HPC specialists most of the time.

One possible runtime execution model for HPC is to propose dynamic scheduling of task graphs combined to message passing models~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359} (to be able to use more than one machine). Those models increase HPC code portability and reach an interesting performance onto heterogeneous architectures, which is interesting to reach exascale programming. At a higher abstraction level, general purpose parallel languages, such as OpenMP~\cite{660313} and OpenCL~\cite{Stone:2010:OPP:622179.1803953} follow the direction of task graph scheduling proposed by those execution models. However, for non-experts end-users, general purpose languages still are difficult to use and to tune for a given application onto a given architecture. The current easiest (with the higher abstraction level), but still efficient, programming model for end-users is Domain Specific Language (DSL). Such a language is specific to the end-user domain and proposes a grammar which is easy to understand. The DSL compiler is able, because of the specific knowledge onto the domain targetted, to automatically apply parallelization and specific optimizations to produce a high performance back-end code. Thus, a DSL is able to split end-user concerns from HPC concerns which is relevant to reach exascale programming models.

However, many DSLs have been proposed for many domains yet, and, as far as we know, only a few of them have been able to reuse work already done by another language~\cite{Sujeeth:2013:CRC:2524984.2524988}. In other words, software engineering properties have to be integrated into DSL conception, such that a new DSL can be seen as a composition of parallelization, optimizations or even languages semantics already proposed by others.

For example, to numerically solve a set of partial differential equations (PDEs), iterative methods are frequently used to approximate the exact solution through a discretized phenomena. A very well known and usual way to discretize PDEs is to transform them to explicit numerical schemes, also often called \emph{stencils}. Many DSLs have been proposed for stencil computations~\cite{spaaTangCKLL11,citeulike12258902,Ragan-Kelley:2013:HLC:2491956.2462176,DeVito:2011:LDS:2063384.2063396,Camier:2015:IPP:2820083.2820107}, as it will be detailed in Section~\ref{sect:rel}. Many of them use same kind of parallelization, data structures or optimizations, however each one has been built from scratch to deal with another additionnal specific case.
We present the Multi-Stencil Language (MSL) DSL, also for stencil-based numerical simulations. MSL is a language with a light grammar to describe a numerical simulation without implementation details. From the description, the compiler has enough information to extract and build an empty parallel pattern of the simulation, which can be filled, in a second step, by implementation concerns. The parallel pattern generated by the language is able to use different existing languages and libraries as it is independent from implementation choices. Moreover, the parallelization performed by the language is large enough to be compatible with many architectures and back-end languages. Contributions presented in this paper are : the computational model of a multi-stencil program and its parallelization formalism; the MSL grammar and its compiler; a back-end implementation and its performance evaluation onto a real case numerical simulation up to 16.384 cores.

Section~\ref{sect:rel} introduces the related work on DSLs for stencils. Section~\ref{sect:formalism} formally explains the targetted domain and its computational model. From this model can be extracted the grammar of MSL in Section~\ref{sect:msl}. Section~\ref{sect:parallelism} shows how parallelism can be extracted from this light grammar of MSL. Sections~\ref{sect:msp} and~\ref{sect:comp} detail choices that have been done in this paper to evaluate MSL, and Section~\ref{sect:eval} shows performance results of the language. Finally, Section~\ref{sect:concl} concludes and proposes perspectives on this work.

>>>>

%As the computation power of modern high performance architectures increases, their heterogeneity and complexity also become more important. For example, the current world's top supercomputer Tianhe-2~\footnote{\url{www.top500.org}} is composed of multi-cores processors and accelerators, and is able to reach a theoretical peak performance around thirty peta floating point operations par seconds. However, to be able to use such a machine, multiple programming models, such as MPI (Message Passing Interface), OpenMP, CUDA etc., and multiple optimization techniques, such as cache or vectorization optimizations, have to be combined. Moreover, current architectures evolution lets think that heterogeneity and complexity in HPC will continue to grow in future.

%One of the big challenges to solve to be able to use exascale computers is to propose programming models which gives access to high performance computing (HPC) to many scientists and not only to a few HPC specialists~\cite{ETP4HPC2013}. Actually, applications which run on supercomputers and which need such a computation power are physics, weather or genomic applications, which are not implemented by HPC specialists most of the time.

%One possible runtime execution model for HPC is to propose dynamic scheduling of task graphs combined to message passing models~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359} (to be able to use more than one machine). Those models increase HPC code portability and reach an interesting performance onto heterogeneous architectures, which is interesting to reach exascale programming. At a higher abstraction level, general purpose parallel languages, such as OpenMP~\cite{660313} and OpenCL~\cite{Stone:2010:OPP:622179.1803953} follow the direction of task graph scheduling proposed by those execution models. However, for non-experts end-users, general purpose languages still are difficult to use and to tune for a given application onto a given architecture. The current easiest (with the higher abstraction level), but still efficient, programming model for end-users is Domain Specific Language (DSL). Such a language is specific to the end-user domain and proposes a grammar which is easy to understand. The DSL compiler is able, because of the specific knowledge onto the domain targetted, to automatically apply parallelization and specific optimizations to produce a high performance back-end code. Thus, a DSL is able to split end-user concerns from HPC concerns which is relevant to reach exascale programming models.

%However, many DSLs have been proposed for many domains yet, and, as far as we know, only a few of them have been able to reuse work already done by another language~\cite{Sujeeth:2013:CRC:2524984.2524988}. In other words, software engineering properties have to be integrated into DSL conception, such that a new DSL can be seen as a composition of parallelization, optimizations or even languages semantics already proposed by others.

%For example, to numerically solve a set of partial differential equations (PDEs), iterative methods are frequently used to approximate the exact solution through a discretized phenomena. A very well known and usual way to discretize PDEs is to transform them to explicit numerical schemes, also often called \emph{stencils}. Many DSLs have been proposed for stencil computations~\cite{spaaTangCKLL11,citeulike12258902,Ragan-Kelley:2013:HLC:2491956.2462176,DeVito:2011:LDS:2063384.2063396,Camier:2015:IPP:2820083.2820107}, as it will be detailed in Section~\ref{sect:rel}. Many of them use same kind of parallelization, data structures or optimizations, however each one has been built from scratch to deal with another additionnal specific case.
%We present the Multi-Stencil Language (MSL) DSL, also for stencil-based numerical simulations. MSL is a language with a light grammar to describe a numerical simulation without implementation details. From the description, the compiler has enough information to extract and build an empty parallel pattern of the simulation, which can be filled, in a second step, by implementation concerns. The parallel pattern generated by the language is able to use different existing languages and libraries as it is independent from implementation choices. Moreover, the parallelization performed by the language is large enough to be compatible with many architectures and back-end languages. Contributions presented in this paper are : the computational model of a multi-stencil program and its parallelization formalism; the MSL grammar and its compiler; a back-end implementation and its performance evaluation onto a real case numerical simulation up to 16.384 cores.

%Section~\ref{sect:rel} introduces the related work on DSLs for stencils. Section~\ref{sect:formalism} formally explains the targetted domain and its computational model. From this model can be extracted the grammar of MSL in Section~\ref{sect:msl}. Section~\ref{sect:parallelism} shows how parallelism can be extracted from this light grammar of MSL. Sections~\ref{sect:msp} and~\ref{sect:comp} detail choices that have been done in this paper to evaluate MSL, and Section~\ref{sect:eval} shows performance results of the language. Finally, Section~\ref{sect:concl} concludes and proposes perspectives on this work.
